Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-10 draft.tex
small edits

Next, recall that to an open set $U \subset M$ the factorization algebra ${\rm Gr} \; \bZ_n (\fg)$ assigns the cochain complex
\[
\clie^\bu\bigg(\fg \otimes \Omega^\bu (U) \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c(U) [1]\right) \bigg) = {\rm Hom}^\bu \bigg(\cliels(\fg \otimes \Omega^\bu(U)) , \cliels (\fg \otimes \Omega^\bu_c(U)) \bigg).
\]
We first define the bracket $\{F,G\}$ between the following simple elements $F : \fg \otimes \Omega^\bu (U)[1] \to k$ and $G : k \to \fg \otimes \Omega^\bu_c(U)[1]$. 
Define $\{F, G\} \in k$ by the composition
\[
k \xto{G} \fg \otimes \Omega^\bu_c(U)[1] \hookrightarrow \fg \otimes \Omega^\bu(U)[1] \xto{F} k
\]
where the middle arrow uses the obvious inclusion of compactly supported de Rham forms inside of all de Rham forms. 
We extend this to a bracket on the full complex by the graded Leibniz rule.

%Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U)[1] \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [1]$. 
%Then, the bracket involving the linear elements $x^* \otimes \alpha$ 
%and $y \otimes \beta$ is defined by
%\begin{align*}
%\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
%\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
%\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
%\end{align*}
%Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. 
%\brian{how to say this now}
\end{proof}

@@

Before stating the definition of this model, we introduce the following variant of the de Rham complex of differential forms on $\RR_{\geq 0}$. 
Let $j : \RR_{>0} \hookrightarrow \RR_{\geq 0}$ be the embedding of the open ray into the closed ray. 
Let $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ be the two-term complex
\[
\Omega^0(\RR_{\geq 0}) \xto{j^* \circ \d_{\rm dR}} \Omega^1(\RR_{>0})[-1]  .
\]
The commutative dg algebra structure on $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ is defined by the rule
\[
f \cdot (g \, \d t) = (j^* f) g\, \d t .
\]

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) .
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg).
\]
%\brian{this is wrong
%\[
%\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
%\]
%}
\end{itemize}
The structure map associated to the embedding 
\begin{equation}\label{eqn:embed}
i : U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\end{equation}
is given by the composition
\[
\begin{tikzcd}
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  \clies\bigg(\fg \otimes \Omega^\bu(V) \otimes \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg) \ar[d, "\simeq"] \\
\clies \bigg(\fg \otimes \left(\Omega^\bu (U) \oplus \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \right) \; , \; \Sym \left(\fg \otimes \left(\Omega^\bu_c(U) [2] \oplus \Omega^\bu_c(V \times [0,\epsilon)) [2]\right)\right) \bigg) \ar[d, "i^* \otimes i_*"] \\
\clies\bigg(\fg \otimes \Omega^\bu(V') \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon'))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V' \times [0,\epsilon'))[2] \right) \bigg).
\end{tikzcd}
\]
%\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d, "\simeq"] \\
%\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d, "i_*"]\\
%\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
The first map uses the fact that the symmetric algebra functor is monoidal. 
The second map is induced from restriction and extension of de Rham forms and compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 
\end{dfn}

@@

Next, we define the $\PP_0$-bracket for the value of the factorization algebra on open sets of the form $V \times [0,\epsilon)$. 
Notice that the underlying graded vector space of $\bC_n(\fg)(V \times [0,\epsilon))$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (V) \otimes \Tilde{\Omega}^\bu ([0,\epsilon))) [1]) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2] \right) \right)  .
\]
We first define the bracket $\{F,G\}$ between the following simple elements 
\[
F : \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \to k
\]
and 
\[
G : k \to \fg \otimes \Omega^\bu_c(V \times [0,\epsilon))[2] .
\]
Define $\{F, G\}$ by the composition
\[
\begin{tikzcd}
k \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[rdd, dotted, "{\{F,G\}}"'] \ar[r, "G \otimes 1"] & 
\bigg(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[d,"{[\cdot, \cdot]}"] \\
& \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \ar[d, "F"] \\ & k
\end{tikzcd}
\]
The middle bracket is induced from the Lie bracket on $\fg$ and the wedge product of differential forms.
Again, this bracket is extended to the full algebra by the Leibniz rule.
\end{proof}

@@

Notice that for an open set $V \subset M$ we have 
\[
\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega (V \otimes \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega_c(V \times \RR_{>0}) [2] \right) \bigg)  .
\]
Integration along $\RR_{>0}$ induces a map of factorization algebras on $M$
\[
I^{\circ} : \bC_n(\fg)^\circ \to {\rm Gr} \; \bZ_n (\fg)
\]
which on linear elements in ${\rm Sym}(\fg \otimes \Omega^\bu_c (V \times \RR_{>0})$ sends $x \otimes \alpha \in \Omega^\bu_c(V \times \RR_{>0})[2]$ to $x \otimes \int_{\RR_{>0}} \alpha \in \Omega^\bu_c (V)[1]$.

Next, using the map $r_\phi$, define a map of factorization algebras
\[
r_\phi^\circ : {\rm Gr} \; \bZ_n (\fg) \to \bC_n(\fg)^\circ
\]
as follows. 
For an open set $V \subset M$, define $r_{\phi}^\circ (V)$ on linear elements $x \otimes \alpha$ in $\Sym(\fg \otimes \Omega^\bu(V)_c[1])$ by
\[
r_\phi^\circ (U) (x \otimes \alpha) = x \otimes (\pi^* \alpha \wedge \phi \d t)  .
\]
This map can be extended to all of ${\rm Gr} \; \bZ_n(\fg)$ in a similar fashion. 
One can show that $r_\phi^\circ$ is a deformation retract of $I^\partial$.
In particular, $I^\partial$ is a quasi-isomorphism of factorization algebras on $M$.

Similarly, integration of compactly supported forms along $\RR_{\geq 0}$ determines a quasi-isomorphism of factorization algebras 
\[
I^\partial : \bC_n(\fg)^\partial \to {\rm Gr} \; \bU_n(\fg) .
\]
Recall that for $V \subset M$ we have
\[
\bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) .
\]
On $V$, the map $I^\partial (V)$ is defined by the composition
\[
\begin{tikzcd}
\clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \otimes \Omega^\bu_c (V)[1] \right) .
\end{tikzcd}
\]
The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})\right)$ and the second map is induced by integration along $\RR_{\geq 0}$. 
It is immediate to check that $I^{\partial}$ extends to a map of factorization algebras.

@@

We have shown that $(I^{\circ}, I^\partial)$ is a quasi-isomorphism of factorization sc-pairs. 
The compatibility of this quasi-isomorphism with Poisson brackets is a direct calculation. 
\end{proof}

>>>>

Next, recall that to an open set $U \subset M$ the factorization algebra ${\rm Gr} \; \bZ_n (\fg)$ assigns the cochain complex
\[
\clie^\bu\bigg(\fg \otimes \Omega^\bu (U) \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c(U) [1]\right) \bigg) = {\rm Hom}^\bu \bigg(\cliels(\fg \otimes \Omega^\bu(U)) , \cliels (\fg \otimes \Omega^\bu_c(U)) \bigg).
\]
We first define the bracket $\{F,G\}$ between the following simple elements $F : \fg \otimes \Omega^\bu (U)[1] \to k$ and $G : k \to \fg \otimes \Omega^\bu_c(U)[1]$. 
Define $\{F, G\} \in k$ by the composition
\[
k \xto{G} \fg \otimes \Omega^\bu_c(U)[1] \hookrightarrow \fg \otimes \Omega^\bu(U)[1] \xto{F} k
\]
where the middle arrow uses the obvious inclusion of compactly supported de Rham forms inside of all de Rham forms. 
We extend this to a bracket on the full complex by the graded Leibniz rule. 
%Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U)[1] \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [1]$. 
%Then, the bracket involving the linear elements $x^* \otimes \alpha$ 
%and $y \otimes \beta$ is defined by
%\begin{align*}
%\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
%\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
%\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
%\end{align*}
%Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. 
%\brian{how to say this now}
\end{proof}

@@

Before stating the definition of this model, we introduce the following variant of the de Rham complex of differential forms on $\RR_{\geq 0}$. 
Let $j : \RR_{>0} \hookrightarrow \RR_{\geq 0}$ be the embedding of the open ray into the closed ray. 
Let $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ be the two-term complex
\[
\Omega^0(\RR_{\geq 0}) \xto{j^* \circ \d_{\rm dR}} \Omega^1(\RR_{>0})[-1]  .
\]
The dg commutative algebra structure on $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ is defined by the formula
\[
f \cdot (g \, \d t) = (j^* f) g\, \d t .
\]

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the constructible factorization algebra on $M \times \RR_{\geq 0}$ where
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg), 
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg).
\]
%\brian{this is wrong
%\[
%\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
%\]
%}
\end{itemize}
The structure map associated to the embedding 
\begin{equation}\label{eqn:embed}
i : U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\end{equation}
is given by the composition
\[
\begin{tikzcd}
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  \clies\bigg(\fg \otimes \Omega^\bu(V) \otimes \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg) \ar[d, "\simeq"] \\
\clies \bigg(\fg \otimes \left(\Omega^\bu (U) \oplus \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \right) \; , \; \Sym \left(\fg \otimes \left(\Omega^\bu_c(U) [2] \oplus \Omega^\bu_c(V \times [0,\epsilon)) [2]\right)\right) \bigg) \ar[d, "i^* \otimes i_*"] \\
\clies\bigg(\fg \otimes \Omega^\bu(V') \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon'))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V' \times [0,\epsilon'))[2] \right) \bigg).
\end{tikzcd}
\]
%\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d, "\simeq"] \\
%\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d, "i_*"]\\
%\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
The first map uses the fact that the symmetric algebra functor is symmetric monoidal. 
The second map is induced from restriction and extension of de Rham forms and compactly supported de Rham forms along the embedding~(\ref{eqn:embed}). 
\end{dfn}

@@

Next, we define the $\PP_0$-bracket for the value of the factorization algebra on open sets of the form $V \times [0,\epsilon)$. 
Notice that the underlying graded vector space of $\bC_n(\fg)(V \times [0,\epsilon))$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (V) \otimes \Tilde{\Omega}^\bu ([0,\epsilon))) [1]) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2] \right) \right)  .
\]
We first define the bracket $\{F,G\}$ between the following simple elements 
\[
F : \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \to k
\]
and 
\[
G : k \to \fg \otimes \Omega^\bu_c(V \times [0,\epsilon))[2] .
\]
Define $\{F, G\}$ by the composition
\[
\begin{tikzcd}
k \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[rdd, dotted, "{\{F,G\}}"'] \ar[r, "G \otimes 1"] & 
\bigg(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[d,"{[\cdot, \cdot] \otimes \wedge}"] \\
& \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \ar[d, "F"] \\ & k
\end{tikzcd}
\]
The middle bracket is induced from the Lie bracket on $\fg$ and the wedge product of differential forms.
Again, this bracket is extended to the full algebra by the Leibniz rule.
\end{proof}

@@

Notice that for an open set $V \subset M$ we have 
\[
\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega (V \times \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega_c(V \times \RR_{>0}) [2] \right) \bigg)  .
\]
Integration along $\RR_{>0}$ induces a map of factorization algebras on $M$
\[
I^{\circ} : \bC_n(\fg)^\circ \to {\rm Gr} \; \bZ_n (\fg)
\]
which on linear elements in ${\rm Sym}(\fg \otimes \Omega^\bu_c (V \times \RR_{>0})$ sends $x \otimes \alpha \in \Omega^\bu_c(V \times \RR_{>0})[2]$ to $x \otimes \int_{\RR_{>0}} \alpha \in \Omega^\bu_c (V)[1]$.

Next, using the map $r_\phi$, wedefine a map of factorization algebras
\[
r_\phi^\circ : {\rm Gr} \; \bZ_n (\fg) \to \bC_n(\fg)^\circ
\]
as follows. 
For an open set $V \subset M$, define $r_{\phi}^\circ (V)$ on linear elements $x \otimes \alpha$ in $\Sym(\fg \otimes \Omega^\bu(V)_c[1])$ by
\[
r_\phi^\circ (U) (x \otimes \alpha) = x \otimes (\pi^* \alpha \wedge \phi \d t)  .
\]
This map can be extended to all of ${\rm Gr} \; \bZ_n(\fg)$ in a similar fashion. 
One can show that $r_\phi^\circ$ is a deformation retract of $I^\partial$.
In particular, $I^\partial$ is a quasi-isomorphism of factorization algebras on $M$.

Similarly, integration of compactly supported forms along $\RR_{\geq 0}$ determines a quasi-isomorphism of factorization algebras 
\[
I^\partial : \bC_n(\fg)^\partial \to {\rm Gr} \; \bU_n(\fg) .
\]
Recall that for $V \subset M$ we have
\[
\bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) .
\]
On $V$, the map $I^\partial (V)$ is defined by the composition
\[
\begin{tikzcd}
\clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \otimes \Omega^\bu_c (V)[1] \right) .
\end{tikzcd}
\]
The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})\right)$ and the second map is induced by integration along $\RR_{\geq 0}$. 
It is quick to check that $I^{\partial}$ extends to a map of factorization algebras.

@@

We have shown that $(I^{\circ}, I^\partial)$ is a quasi-isomorphism of factorization sc-pairs. 
A direct calculation verifies that this quasi-isomorphism respects Poisson brackets. 
\end{proof}
